R for Clinical Study Reports and Submission

### 2021-08-27 intro.Rmd

In clinical trial development, developer needs to organize source code to deliver SDTM or ADaM datasets and table, listing and figures (TLFs).
For example, a Phase 3 clinical trial typically require hundreds of TLFs. 
A consistent and well-defined folder structure is crucial to manage a clinical trial analysis and reporting (A&R) project.

We recommend to use R package folder structure to organize all the analysis and reporting related source code and documentation
for a clinical trial A&R project. 
By using the R package folder structure you can follow the convention to organize your code as other contributors on CRAN.
The consistent approach simplify the communication for developers within and across organizations.

>>>>

In clinical trial development, developers needs to organize source code to deliver Study Data Tabulation Model (SDTM) or Analysis Dataset Model (ADaM) datasets and table, listing and figures (TLFs).
For example, a Phase 3 clinical trial typically require hundreds of TLFs. 
A consistent and well-defined folder structure is crucial to manage a clinical trial analysis and reporting (A&R) project.

We recommend to use R package folder structure to organize all the A&R related source code and documentation for a clinical trial A&R project. 
By using the R package folder structure, you can follow the convention to organize your code as other contributors on CRAN.
This consistent approach simplifies the communication for all developers within and across organizations.

### 2021-08-27 tlf-overview.Rmd
add clarification for tables

A typical CSR contain full details of an individual clinical study 
including clinical and statistical description, presentations, and analyses. 
A large number of tables and figures are incorporated into the main text and appendices 
of a CSR. In CDISC pilot project, an [example CSR](file:///C:/Users/zhanyilo/OneDrive%20-%20Merck%20Sharp%20&%20Dohme,%20Corp/Desktop/cdiscpilot01.pdf) is also provided. If you are interested in more examples of clinical study reports, 
the European Medicines Agency (EMA) publishes clinical data including 
clinical study reports submitted by pharmaceutical companies 
on [EMA clincal data website](https://clinicaldata.ema.europa.eu/web/cdp/home).

Building CSR is a team work with clinicians, medical writers, statisticians and statistical programmers.
Here, We focus on the work and deliverables completed by statisticians and statistical programmers. 
In an organization, A group of statisticians and statistical programmers commonly work together to 
define, develop, validate and deliver tables, listings and figures (TLFs) required for a CSR.
Microsoft Word is widely used to prepare CSR in pharmaceutical industry. 
Therefore, `rtf`, `doc`, `docx` are commonly used format to deliver TLFs.

@@

- title, subtitle
- footnote, data source
- special character
- etc

@@

There are other R packages that can achieve similar goals.
Interested reader can refer "Microsoft/LibreOffice Formats" section in 
[CRAN Task View: Reproducible Research](https://cran.r-project.org/web/views/ReproducibleResearch.html)
for an overview.

>>>>

A typical CSR contain full details of an individual clinical study 
including clinical and statistical description, presentations, and analyses. 
A large number of tables and figures are incorporated into the main text and appendices 
of a CSR. In CDISC pilot project, an [example CSR](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse/updated-pilot-submission-package/900172/m5/53-clin-stud-rep/535-rep-effic-safety-stud/5351-stud-rep-contr/cdiscpilot01/cdiscpilot01.pdf) 
is also provided. If you are interested in more examples of clinical study reports, 
the European Medicines Agency (EMA) publishes clinical data including 
clinical study reports submitted by pharmaceutical companies 
on [EMA clincal data website](https://clinicaldata.ema.europa.eu/web/cdp/home).

Building CSR is a team work with clinicians, medical writers, statisticians and statistical programmers.
Here, we focus on the work and deliverables completed by statisticians and statistical programmers. 
In an organization, A group of statisticians and statistical programmers commonly work together to 
define, develop, validate and deliver tables, listings and figures (TLFs) required for a CSR.
Microsoft Word is widely used to prepare CSR in pharmaceutical industry. 
Therefore, `rtf`, `doc`, `docx` are commonly used format to deliver TLFs.

@@

- title, subtitle
- footnote, data source
- special character
- etc.

@@

There are other R packages that can create TLFs in `.rtf` or `.docx` format.
Interested reader can refer "Microsoft/LibreOffice Formats" section in 
[CRAN Task View: Reproducible Research](https://cran.r-project.org/web/views/ReproducibleResearch.html)
for an overview.
